Space-time adaptivity for parabolic evolution equations

### 2020-05-18 Latex/paper.tex
current state

\subsection{First singular solution}
Selecting the L-shaped domain $\Omega := [-1,1]^2 \setminus [0,1]^2$ with data
$u_0 \equiv 0$ and $g(x,y) := \bbone_{{x^2 + y^2 \leq 1/4}}(x,y)$, the true
solution is unknown in closed form but known to be singular in the re-entrant
corner.\jw{is het wel singulier? of alleen minder regulier? hier wil ik een citatie of *iets* anders} Figure~\ref{fig:cylinder}
shows the error progression

\begin{itemize}
  \item Adaptive vs full vs sparse grid
  \item Misschien de spatial meshes voor wat verschillende $\lambda$, of sowieso
    tellen hoeveel $\lambda$'s er zijn in dit geval? lijkt veel op de numres van FK19
\end{itemize}
\begin{figure}
  \includegraphics[width=0.5\linewidth]{cylinder_adaptive_errors}
  \caption{Error progression of $e^\delta := u - u^{\underline{\delta}\delta}$ for the cylinder problem as
  a function of $\dim X^\delta$ for adaptive and full grid refinement.\jw{excuse the terrible graph}}
  \label{fig:cylinder}
\end{figure}

>>>>

\subsection{First singular solution}
Selecting the L-shaped domain $\Omega := [-1,1]^2 \setminus [0,1]^2$ with data
$u_0 \equiv 0$ and $g(x,y) := \bbone_{{x^2 + y^2 \leq 1/4}}(x,y)$, the true
solution is unknown in closed form but known to be singular in the re-entrant
corner.\jw{is het wel singulier? of alleen minder regulier? hier wil ik een citatie of *iets* anders}
Figure~\ref{fig:cylinder} shows the error progression for this cylinder problem.
We see that the full grid rate of $1/4$ is improved to $1/2$ for adaptive refinement,
and again note the superconvergent rate for the time-slice error at $t=0$.
\begin{itemize}
  \item Adaptive vs full vs sparse grid
  \item Misschien de spatial meshes voor wat verschillende $\lambda$, of sowieso
    tellen hoeveel $\lambda$'s er zijn in dit geval? lijkt veel op de numres van FK19
\end{itemize}
\begin{figure}
  \includegraphics[width=0.5\linewidth]{cylinder_adaptive_errors}
  \caption{Error progression of $e^\delta := u - u^{\underline{\delta}\delta}$ for the cylinder problem as
  a function of $\dim X^\delta$ for adaptive and full grid refinement.\jw{excuse the terrible graph}}
  \label{fig:cylinder}
\end{figure}
